A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/abstract.tex
change name title

Submitted to the Department of Electrical Engineering and Computer Science \\
in partial fulfillment of the requirements for the degree of \\
Doctor of Philosophy \\ % <--- replace this with Master of Science if you want a master's instead
\end{center}

@@

\noindent\rule[0.5ex]{2in}{1pt} \\
Thesis Supervisor: Your first advisor's name goes here \\
Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science

\vspace{.1in}

\noindent Thesis Supervisor: Your second advisor's name goes here \\
Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science

>>>>

Submitted to the Department of Electrical Engineering and Computer Science \\
in partial fulfillment of the requirements for the degree of \\
Master of Science \\ % <--- replace this with Master of Science if you want a master's instead
\end{center}

@@

\noindent\rule[0.5ex]{2in}{1pt} \\
Thesis Supervisor: Wojciech Matusik\\
Title:  Associate Professor of Electrical Engineering and Computer Science

%\vspace{.1in}

%\noindent Thesis Supervisor: Your second advisor's name goes here \\
%Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science
